CdGF_aucrf

### 2016-10-05 code/CdGF_AUCRF.Rmd
clean up ROC plot file

```{r roc, fig.width=8, fig.height=8, results= 'hide'}
#create dataframe for RF-classification
meta_file$Euth_Early <- factor(ifelse(meta_file[ , 'Early_Euth'] == FALSE, 1, 0))

@@

```{r importance, fig.width=10, fig.height=5}

#Importance Plot
#n_rf_features <- 9
euth_otus <- euth_otu_feat#[1:n_rf_features]
euth_tax <- get_tax(1, euth_otus, tax_file)
euth_tax$tax_label <- paste(euth_tax$tax, ' (', 
                            gsub('tu0*', 'TU ', rownames(euth_tax)), 
                                   ') : ', round(rf_early_aucrf$ranking[euth_otus], 3), sep = '')

RF_features_polt <- Predict_early_euth_df %>% 
  select(Euth_Early, one_of(euth_otus)) %>% 
  gather('OTU', 'Value', -Euth_Early) %>% 
  full_join(data.frame(OTU = names(rf_early_aucrf$ranking[euth_otus]), 
               MDA =  rf_early_aucrf$ranking[euth_otus])) %>% 
  ggplot( aes(x = reorder(factor(OTU), MDA), y = Value, fill = Euth_Early, dodge = Euth_Early)) +
  theme(legend.title=element_blank(), legend.position = c(0.9,0.5),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = NA),
        panel.grid.minor = element_line(colour = NA)) +
  geom_point(pch = 21, position = position_jitterdodge(), alpha = 0.4, size = 2) + coord_flip() +
  scale_x_discrete(breaks = rownames(euth_tax), labels = euth_tax$tax_label) +
  stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median,
                 geom = "crossbar", width = 0.6, position=position_dodge(width=0.8)) + 
  scale_fill_manual(values = c('red', 'black'), labels = c('Severe','Mild'),
                    guide = guide_legend(reverse=TRUE))

RF_features_polt + labs( y = 'Relative Abundance (%)\nClassification (OTU) : MDA', x = '', title = '')

RF_features_polt + labs( y = 'Relative Abundance (%) - log10\nClassification (OTU) : MDA', x = '', title = '') +
  scale_y_log10()
```

### Partial Dependency Plots
###### Using optimal RF model generated from whole dataset

```{r partial dependence, fig.width=10, fig.height=10}
layout(matrix(c(1:9), nrow=3, byrow=TRUE))

partial_otu <- c()
for (i in seq_along(euth_otu_feat)) {
  partial_otu <- partialPlot(rf_early_aucrf$RFopt, aucrf_data, euth_otu_feat[i], xlab='',
                main=paste(euth_tax$tax_label[i]))
points(Predict_early_euth_df[Predict_early_euth_df$Euth_Early == 0 ,euth_otu_feat[i]], 
       jitter(rep(0.75*(diff(range(partial_otu$y))) + min(partial_otu$y), 
                  sum(Predict_early_euth_df$Euth_Early == 0)), 
              amount = (0.1*(diff(range(partial_otu$y))))), 
              pch = 21, bg = 'red')
points(Predict_early_euth_df[Predict_early_euth_df$Euth_Early == 1 ,euth_otu_feat[i]], 
       jitter(rep(0.25*(diff(range(partial_otu$y))) + min(partial_otu$y), 
                  sum(Predict_early_euth_df$Euth_Early == 1)), 
              amount = (0.1*(diff(range(partial_otu$y))))), 
              pch = 21, bg = 'gray')
}

```

>>>>

```{r roc, fig.width=8, fig.height=8, results= 'hide'}
#create dataframe for RF-classification
meta_file$Euth_Early <- factor(ifelse(meta_file[ , 'Early_Euth'] == FALSE, 0, 1))

@@

### Partial Dependency with Relative Abundance Overlayed Plots
###### Using optimal RF model generated from whole dataset
###### Plot labels contain MDA of each OTU

```{r rel abund partial depend, fig.width=10, fig.height=10}

#n_rf_features <- 9
#euth_otus <- euth_otu_feat[1:n_rf_features]
euth_tax <- get_tax(1, euth_otu_feat, tax_file)
euth_tax$tax_label <- paste(euth_tax$tax, ' (', 
                            gsub('tu0*', 'TU ', rownames(euth_tax)), 
                                   ') : ', round(rf_early_aucrf$ranking[euth_otu_feat], 3), sep = '')

layout(matrix(c(1:9), ncol=3, byrow=TRUE))

for (i in seq_along(euth_otu_feat)) {
  partial_otu <- partialPlot(rf_early_aucrf$RFopt, aucrf_data, euth_otu_feat[i], xlab='',
                main=paste(euth_tax$tax_label[i]))
points(Predict_early_euth_df[Predict_early_euth_df$Euth_Early == 1 ,euth_otu_feat[i]], 
       jitter(rep(0.25*(diff(range(partial_otu$y))) + min(partial_otu$y), 
                  sum(Predict_early_euth_df$Euth_Early == 1)), 
              amount = (0.1*(diff(range(partial_otu$y))))), 
              pch = 21, bg = 'red')
points(Predict_early_euth_df[Predict_early_euth_df$Euth_Early == 0 ,euth_otu_feat[i]], 
       jitter(rep(0.75*(diff(range(partial_otu$y))) + min(partial_otu$y), 
                  sum(Predict_early_euth_df$Euth_Early == 0)), 
              amount = (0.1*(diff(range(partial_otu$y))))), 
              pch = 21, bg = 'gray')
}
plot(NULL, xlim = c(0,1), ylim = c(0,1), xlab = '', ylab = '', axes = F)
legend('topleft', c('Mild', 'Severe'), pch = 21, pt.bg = c('gray','red'), cex = 2)
```
